---
title: "TMDB Prediction - R-Collab"
author: "Mike and Goutham"
date: "September 22, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# TMDB Predict - R Collab

## 1. Data loading and cleaning

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(jsonlite)

```

```{r data loading}
data <- read_csv("train.csv")
print(data)
```

We load our initial data as a tibble, and start inspecting it. As a tibble, we can safely load it and it just gives us the first ten rows with color-coded information on column types.

Let's start with looking at the "genres" column, and seeing if this is correctly formed json we can play with.

```{r genres}

genres <- data$genres
genres <- gsub("\'","\"", genres)
genres <- na.omit(genres)

parsed.genres <- lapply(genres, fromJSON)
print(head(parsed.genres))

```

The JSON parses doesn't deal with NAs very well, and so this data loses the 7 rows where the genres are NA.  This can possible be dealt with later, but we're on track.




## 2. Exploratory Data Analysis

## 3. Feature Engineering

## 4. Prediction 1

## 5. Validation 1

## 6. Prediction 2

## 7. Validation 2

<!-- and so on... -->

